```{r}
#1a.
gamblersRuin <- function(n1, n2, p) {
  len <- 0
  repeat {
    len <- len + 1
    result <- rbinom(1, 1, p)
    if(result == 1) {
      n1 <- n1 + 1
      n2 <- n2 - 1
    }
    else {
      n1 <- n1 - 1
      n2 <- n2 + 1
    }
    if(n1 == 0 || n2 ==0) {
      break
    }
  }
  return(c('len' = len, 'n1' = n1, 'n2' = n2))
}
set.seed(2017)
gamblersRuin(n1 = 10, n2 = 10, p = 0.5)
```

```{r}
#1b.
res <- matrix(nrow = 10000, ncol = 3)
for(n in 1:10000) {
  res[n, ] <- gamblersRuin(n1 = 5, n2 = 10, p = 0.5)
}
head(res, 10)
```

```{r}
#1c.
onebroke <- nrow(res[res[, 2] == 0, ]) / 10000
onebroke
ntoss <- mean(res[ , 1])
ntoss
```
My first result is 0.6675, which is approximately 2/3.
My second result is 51.0237, which is close to 50.

```{r}
#1d.
res1 <- matrix(nrow = 10000, ncol = 3)
for(n in 1:10000) {
  res1[n, ] <- gamblersRuin(n1 = 5, n2 = 10000, p = 0.49)
}
head(res1, 10)
onebroke1 <- nrow(res1[res1[, 2] == 0, ]) / 10000
onebroke1
ntoss1 <- mean(res1[ , 1])
ntoss1
```

```{r}
#2a.

#i.
colSumsFor <- function(x) {
  v <- vector(length = ncol(x)) 
  for (n in 1:ncol(x)) {
      v[n] <- sum(x[ ,n])
  }
  v
}

#ii.
colSumsFor2 <- function(x) {
  x <- as.matrix(x)
  v <- vector(length = ncol(x))
  for(n in 1:ncol(x)) {
    v[n] <- sum(x[ ,n])
  }
  v
}

#iii.
colSumsApply <- function(x) {
  apply(as.matrix(x), 2, sum)
}

#iv.
colSumsSapply <- function(x) {
  sapply(as.data.frame(x), sum)
}

#v.
colSumsLapply <- function(x) {
  do.call(cbind, lapply(as.data.frame(x), sum))
}

#vi.
colSumsCrossprod <- function(x) {
  crossprod(rep(1, nrow(x)), as.matrix(x))[1, ]
} 

mat <- as.matrix(iris[, 1:4]) 
df <- iris[, 1:4]

colSumsFor(mat)
colSumsFor2(mat)
colSumsApply(mat)
colSumsSapply(mat)
colSumsLapply(mat)
colSumsCrossprod(mat)
colSums(mat)
```

```{r}
#2b.
df <- as.data.frame(matrix(rnorm(5000), 50, 100))
colSumsDf <- rbind(colSumsFor = system.time(replicate(n = 10000, colSumsFor(df))), 
                   colSumsFor2 = system.time(replicate(n = 10000, colSumsFor2(df))), 
                   colSumsApply = system.time(replicate(n = 10000, colSumsApply(df))), 
                   colSumsSapply = system.time(replicate(n = 10000, colSumsSapply(df))), 
                   colSumsLapply = system.time(replicate(n = 10000, colSumsLapply(df))), 
                   colSumsCrossprod = system.time(replicate(n = 10000, colSumsCrossprod(df))),
                   colSums = system.time(replicate(n = 10000, colSums(df))))
colSumsDf
```
So colSumsLapply is the fastest one, and colSumsFor is the slowest one.

```{r}
#2c.
mat <- matrix(rnorm(5000), 50, 100)
colSumsMat <- rbind(colSumsFor = system.time(replicate(n = 10000, colSumsFor(mat))),
                    colSumsFor2 = system.time(replicate(n = 10000, colSumsFor2(mat))), 
                    colSumsApply = system.time(replicate(n = 10000, colSumsApply(mat))), 
                    colSumsSapply = system.time(replicate(n = 10000, colSumsSapply(mat))), 
                    colSumsLapply = system.time(replicate(n = 10000, colSumsLapply(mat))), 
                    colSumsCrossprod = system.time(replicate(n = 10000, colSumsCrossprod(mat))),
                    colSums = system.time(replicate(n = 10000, colSums(mat))))
colSumsMat                                                                  
```
So colSums is the fastest one, and colSumsSapply is the slowest one.
No, the order is different.

```{r}
#3a.
subiris <- iris[50:150, ]
fit <- lm(Sepal.Length ~ Petal.Length, data = subiris)
summary(fit)
```
The intercept is 3.23649, and the slope is 0.61853.
Multiple R-squared is 0.676.

```{r}
#3b.
coefs <- coef(fit)
plot(subiris$Sepal.Length ~ subiris$Petal.Length, xlab = 'Petal.Length', ylab = 'Sepal.Length', cex = 0.8)
abline(coefs)
```

```{r}
#3c.
par(mfrow = c(2, 2))
plot(fit, 1, id.n = 3)
plot(fit, 2, id.n = 3)
plot(fit, 3, id.n = 3)
plot(fit, 5, id.n = 3)
```

id.n equals to 3.
point 58 is an outlier and point 1, 2 are high leverage points.

```{r}
#3d.
fitted <- fit$fitted.values
residual <- fit$residuals
plot(fitted, residual, xlab = 'fitted.values', ylab = 'residuals', cex = 0.8)
```

```{r}
#3e.
y <- subiris$Sepal.Length
1 - (var(residual)) / var(y)
```











